---
title: "How to setup DDModeling in R-Studio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DDModeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, eval= TRUE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Requirements
To ensure the full functionality of DDModeling it is recommended to use it with an updated installation of Windows 10. Although it is possible to use the package under Linux or macOS, no tests have been conducted regarding usability and trustworthiness under these operating systems.

# Installation prerequisites
DDModeling is distributed through GitHub. Although a submission to CRAN is planned, it has a low priority and may take some time. The easiest way to install packages from GitHub is to use the _install_github_ function found in the **devtools** package. Therefore, installation of the **devtools** package is required:

```{r eval= FALSE}
install.packages("devtools")
```

However, since the DDModeling package relies heavily on the use of C++ code, some of this code must be compiled during the installation process. Therefore a C++ compiler is also required. It is recommended to install the latest version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/) and to stick to the standard installation. This should guarantee a successful C++ compilation not only for the DDModeling package but also for any other R package that uses C++ code.

# Installation
When all this is done, there is only one more line to enter:

```{r eval= FALSE}
devtools::install_github("Pelzer402/DDModeling")
```

If the installation was successful, you are ready to start using all kinds of fancy model definitions and fit procedures! Take a look at the Tutorials tab at the top of this website to learn more about using the DDModeling package.

# Updating

If you want to update your version of DDModeling, you can do so simply by following the steps above. However, I would advise you to delete your previous installation of DDModeling first!

