---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DDModeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, eval= TRUE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Importing data into DDModeling is done by calling the function `DDRep()` which takes two arguments **model** and **data**. **model** represents a **DDModel** object (see [here](Model_definition.html) for a tutorial). **raw** specifies the raw data from a given experiment. For a successful import, **raw** must follow a formatting convention. This convention is examined in the following section.

# How to format RAW data

The raw data in the DDModeling package is handled in data.frames, which contain three coulmns:

* **cond** (factor): Specifies the condition under which a given trial was performed
* **resp** (numeric): Specifies the binary coded response property of a study 
* **time** (numeric): Indicates the time (in rounded ms) for a given trial

The naming convention within the **cond** could be free, but you must ensure that the factor names match the **model** within the `DDRep()` function, which means that the conditions specified in the **model** must match those in your data! **resp** on the other hand follows a uniform coding scheme: The value 0 represents an attempt that led to an error (i.e. wrong answer) and the value 1 represents an attempt that led to a success (i.e. correct answer). The **time** must be given in rounded millisecond format, i.e. only natural numbers are allowed. 

For demonstration purposes, DDModeling comes with a predefined data set **FLANKER_DATA** representing 64 data sets (i.e. subjects) of a flanker task experiment with 320 experiments per condition. If you want to import data into DDModeling, your data should look like this


```{r}
library(DDModeling)
head(FLANKER_DATA[[1]])
```

# How to import data

After you formated your data according to the above conventions and constructed an according **DDModel** importing it is rather simple.

```{r}
DSTP <- DDModel(model="DSTP",task = "flanker",CDF_perc = c(0.1,0.3,0.5,0.7,0.9), CAF_perc = c(0.0,0.2,0.4,0.6,0.8,1.0))
Subj <- DDRep(model = DSTP,raw = FLANKER_DATA[[1]])
```

Finally you can take a look at your imported data simply by calling the object or using the `plot()` function.

```{r}
Subj
plot(Subj)
```


