---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DDModeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, eval= TRUE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Importing data in DDModeling is done by calling the `DDRep()` function, which needs two arguments **model** and **data**. **model** constitutes a **DDModel** object (see [here](Model_definition.html) for a tutorial). **raw** specifies the raw data from a given experiment. For a sucessfull import, **raw** needs to follow a formating convention. This convention will be investigated in the following section.

# How to format RAW data

Raw data in the DDModeling package is handled in data.frames containing three coulmns:

* **cond** (Factor): Specifying the condition under which a given trial was taken
* **resp** (Numeric): Specifying the binary coded response property of a trial 
* **time** (Numeric): Specifying the time (in rounded ms) for a given trial

The naming convention inside the **cond** coulmn is free, however you have to make sure that the factor labels correspond to the **model** inside the `DDRep()` function, meaning that the conditions specified in the **model** need to match those in your data! **resp** on the other hand follows a unified coding scheme: The value 0 represents a trial that resulted in an error (i.e. wrong response) and the value 1 represents a trial that resulted in a success (i.e. correct response). **time** has to be in the format of rounded milliseconds, meaning only natural numbers are allowed. 

For demonstration purposes DDModeling comes equipped with a predefined dataset **FLANKER_DATA**, which constitutes 64 datasets (i.e. subjects) of a flanker task experiment with 320 trials per condition. If you want to import data into DDModeling your data should look something like this

```{r}
library(DDModeling)
head(FLANKER_DATA[[1]])
```

# How to import data

After you formated your data according to the above conventions and constructed an according **DDModel** importing it is rather simple.

```{r}
DSTP <- DDModel(model="DSTP",task = "flanker",CDF_perc = c(0.1,0.3,0.5,0.7,0.9), CAF_perc = c(0.0,0.2,0.4,0.6,0.8,1.0))
Subj <- DDRep(model = DSTP,raw = FLANKER_DATA[[1]])
```

Finally you can take a look at your imported data simply by calling the object or using the `plot()` function.

```{r}
Subj
plot(Subj)
```


