---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DDModeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE, eval= TRUE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# How to simulate in DDModeling
To simulate data in DDModeling, you need a specified **DDModel** (see [here](Model_definition.html) for a tutorial).

```{r}
library(DDModeling)
DSTP <- DDModel(model="DSTP",task = "flanker",CDF_perc = c(0.1,0.3,0.5,0.7,0.9),CAF_perc = c(0.0,0.2,0.4,0.6,0.8,1.0))
```

With this model the simulation using `Sim_DDModel()` is uncomplicated.

```{r}
some_data <- Sim_DDModel(model=DSTP,trials = 1000L)
```

`Sim_DDModel()` requires at least two arguments **model** and **trials**. The former specifies a **DDModel** object, the latter the number of trials per condition to be simulated. It then returns a **DDRep** object, which can be inspected by simply calling it:

```{r}
some_data
```

or using `plot()`

```{r}
plot(some_data)
```

Note that `Sim_DDModel()` initializes a simulation randomly by default, which means that the parameters within the model used for the simulation are uniformly drawn from the parameter domains specified in the model. If you want to run a simulation with specific parameter values, you must specify the parameters under the **parameter** argument! This argument requires a data.frame whose column names must be identical (in name and order!) to the parameters specified in the model!

```{r}
custom_parameter <- data.frame(Ter= 0.2, a= 0.17, c=0.18 ,mu_t= 0.08, mu_f= 0.09, mu_RS2= 0.29, mu_SS= 0.5)
custom_data <- Sim_DDModel(model = DSTP,trials = 1000L,parameter = custom_parameter)
custom_data@PAR
plot(custom_data)
```

If you want to run several simulations with different parameters, just add rows to your data.frame! If you need multiple samples of these simulations, specify the **simulations** argument. Note, however, that `Sim_DDModel()` then returns a list of **DDRep** objects! If you do not specify the **parameter** argument, simulations=n>1 will result in n randomly drawn parameters as in the example above; but if you do specify it, simulations=n will result in n simulations for each parameter set!
